Text S1. Further details on the semi-mechanistic forecasting models

### 2023-12-11 manuscript/final submission/Supplementary/S10-Table.tex

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended
% to minimize problems and delays during our production
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% Once your paper is accepted for publication,
% PLEASE REMOVE ALL TRACKED CHANGES in this file
% and leave only the final text of your manuscript.
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file.
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment.
%
% Please add line breaks to long display equations when possible in order to fit size of the column.
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
% \usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace}
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
% \bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{lineno}
\usepackage[T1]{fontenc}
\linenumbers
\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\usepackage{forarray}
\usepackage{xstring}
\newcommand{\getIndex}[2]{
  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
}

\setcounter{secnumdepth}{0}

\newcommand{\getAff}[1]{
  \getIndex{#1}{London School of Hygiene \& Tropical Medicine,Karlsruhe
Institute of Technology Institute of Economic Theory and Statistics,Max
Planck Institute for Multidisciplinary Sciences,UK Health Security
Agency,Imperial College London}
}

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Comparing human and model-based forecasts of COVID-19 in
Germany and
Poland} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Nikos I. Bosse\textsuperscript{\getAff{London School of Hygiene \&
Tropical Medicine}}\textsuperscript{*},
Sam Abbott\textsuperscript{\getAff{London School of Hygiene \& Tropical
Medicine}},
Johannes Bracher\textsuperscript{\getAff{Karlsruhe Institute of
Technology Institute of Economic Theory and Statistics}},
Habakuk Hain\textsuperscript{\getAff{Max Planck Institute for
Multidisciplinary Sciences}},
Billy J. Quilty\textsuperscript{\getAff{London School of Hygiene \&
Tropical Medicine}},
Mark Jit\textsuperscript{\getAff{London School of Hygiene \& Tropical
Medicine}},
Centre for the Mathematical Modelling of Infectious Diseases COVID-19
Working Group\textsuperscript{\getAff{London School of Hygiene \&
Tropical Medicine}},
Edwin van Leeuwen\textsuperscript{\getAff{UK Health Security
Agency}, \getAff{London School of Hygiene \& Tropical Medicine}},
Anne Cori\textsuperscript{\getAff{Imperial College London}},
Sebastian Funk\textsuperscript{\getAff{London School of Hygiene \&
Tropical Medicine}}\\
\bigskip
\textbf{\getAff{London School of Hygiene \& Tropical Medicine}}London
School of Hygiene \& Tropical Medicine, Keppel Street, London WC1E7HT,
United Kingdom\\
\textbf{\getAff{Karlsruhe Institute of Technology Institute of Economic
Theory and Statistics}}Karlsruhe Institute of Technology - Institute of
Economic Theory and Statistics, Post Box 6980, 76049 Karlsruhe,
Germany\\
\textbf{\getAff{Max Planck Institute for Multidisciplinary Sciences}}Max
Planck Institute for Multidisciplinary Sciences, Am Faßberg 11, 37077
Göttingen, Germany\\
\textbf{\getAff{UK Health Security Agency}}UK Health Security Agency,
London NW9 5EQ, United Kingdom\\
\textbf{\getAff{Imperial College London}}Imperial College London,
Norfolk Place, London W2 1PG, United Kingdom\\
\bigskip
* Corresponding author: nikos.bosse@lshtm.ac.uk\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Forecasts based on epidemiological modelling have played an important
role in shaping public policy throughout the COVID-19 pandemic. This
modelling combines knowledge about infectious disease dynamics with the
subjective opinion of the researcher who develops and refines the model
and often also adjusts model outputs. Developing a forecast model is
difficult, resource- and time-consuming. It is therefore worth asking
what modelling is able to add beyond the subjective opinion of the
researcher alone. To investigate this, we analysed different real-time
forecasts of cases of and deaths from COVID-19 in Germany and Poland
over a 1-4 week horizon submitted to the German and Polish Forecast Hub.
We compared crowd forecasts elicited from researchers and volunteers,
against a) forecasts from two semi-mechanistic models based on common
epidemiological assumptions and b) the ensemble of all other models
submitted to the Forecast Hub. We found crowd forecasts, despite being
overconfident, to outperform all other methods across all forecast
horizons when forecasting cases (weighted interval score relative to the
Hub ensemble 2 weeks ahead: 0.89). Forecasts based on computational
models performed comparably better when predicting deaths (rel. WIS
1.26), suggesting that epidemiological modelling and human judgement can
complement each other in important ways.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.
\section*{Author summary}
Mathematical models of COVID-19 have played a key role in informing
governments across the world. While mathematical models are informed by
our knowledge of infectious disease dynamics, they are ultimately
developed and iteratively adjusted by the researchers and shaped by
their subjective opinions. To investigate what modelling is able to add
beyond the subjective opinion of the researcher alone, we compared human
forecasts with model-based predictions of COVID-19 cases and deaths
submitted to the so-called German/Polish Forecast Hub (which collates a
variety of models from a range of teams). \textbar{} We found that our
human forecasts consistently outperformed an aggregate of all available
model-based forecasts when predicting cases, but not when predicting
deaths. Our findings suggest that human insight may be most valuable
when forecasting highly uncertain quantities, which depend on many
factors that are hard to model using equations, while mathematical
models may be most useful in settings like predicting deaths, where
leading indicators with a clear connection to the target variable are
available. This potentially has very relevant policy implications, as
agencies informing policy-makers could benefit from routinely eliciting
human forecasts in addition to model-based predictions to inform
policies.

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Infectious disease modelling has a long tradition and has helped inform
public health decisions both through scenario modelling, as well as
actual forecasts of (among others) influenza {[}e.g. 1,2--4{]}, dengue
fever {[}e.g. 5,6,7{]}, ebola {[}e.g. 8,9{]}, chikungunya {[}e.g.
10,11{]} and now COVID-19 {[}e.g. 12,13--17{]}. Applications of
epidemiological models differ in the way they make statements about the
future. Forecasts aim to predict the future as it will occur, while
scenario modelling and projections aim to represent what the future
could look like under certain scenario assumptions or if conditions
stayed the same as they were in the past. Forecasts can be judged by
comparing them against observed data. Since it is much harder to fairly
assess the accuracy and usefulness of projections and scenario modelling
in the same way, this work focuses on forecasts, which represent only a
subset of all epidemiological modelling.

Since March 2020, forecasts of COVID-19 from multiple teams have been
collected, aggregated and compared by Forecast Hubs such as the US
Forecast Hub {[}13,14{]}, the German and Polish Forecast Hub {[}15,16{]}
and the European Forecast Hub {[}17{]}. Often, different individual
forecasts are combined into a single forecast, e.g.~by taking the mean
or median of all forecasts. These ensemble forecasts usually tend to
perform better and more consistently than individual forecasts (see e.g.
{[}6{]}; {[}18{]}).

Individual computational models usually rely to varying degrees on
mechanistic assumptions about infectious disease dynamics (such as
SIR-type compartmental models that aim to represent how individuals move
from being susceptible to infected and then recovered or dead). Some are
more statistical in nature (such as time series models that detect
statistical patterns without explicitly modelling disease dynamics). How
exactly such a mathematical or computational model is constructed and
which assumptions are made depends on subjective opinion and judgement
of the researcher who develops and refines the model. Models are
commonly adjusted and improved based on whether the model output looks
plausible to the researchers involved.

The process of model construction and refinement is laborious and
time-consuming, and it is therefore worth asking what modelling can add
beyond the subjective judgment of the researcher alone. In this work, we
ask this question specifically in the context of predictive performance,
and set aside other advantages of epidemiological modelling (such as
reproducibility or the ability to obtain a deeper fundamental
understanding of how diseases spread). One natural way to do this is to
compare the predictive performance of forecasts based on computational
models (``model-based forecasts'') against forecasts made by individual
humans without explicit use of a computer model (``direct human
forecasts'') or a combination of multiple such forecasts (``crowd
forecasts'').

Previous work has examined such direct human forecasts in various
contexts, such as geopolitics {[}19,20{]}, meta-science {[}21,22{]},
sports {[}23{]} and epidemiology {[}11,24,25{]}. Several prediction
platforms {[}26--28{]} and prediction markets {[}29{]} have been created
to collate expert and non-expert predictions. However, with the notable
exception of {[}11{]}, these forecasts were not designed to be evaluated
alongside model-based forecasts and usually follow their own (often
binary) prediction formats. Direct human forecasts may be able to take
into account insights and relationships between variables which are hard
to specify using epidemiological models. However, it is not entirely
clear in which situations human forecasts perform well or badly. For
example, {[}11{]} found that humans could outperform computer models at
predicting the 2014/15 and 2015/16 flu season in the US, a setting where
the disease was well known and information about previous seasons was
available. However, humans tended to do slightly worse at predicting the
2014/15 outbreak of chikungunya in the Americas, a disease previously
largely unobserved and unknown in these regions at the time.

In this study, we analyse the performance of direct human forecasts
relative to model-based forecasts and discuss the added benefit of
epidemiological modelling over human judgement alone. As a case study,
we use different forecasts, involving varying degrees of human
intervention, which we submitted in real time to the German and Polish
Forecast Hub. In contrast to {[}11{]} we elicited not only point
predictions, but full predictive distributions (``probabilistic
forecasts'', see e.g. {[}30{]}) from participants. This allows us to
compare not only predictive accuracy, but also how well human
forecasters and model-based forecasts were able to quantify forecast
uncertainty.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We created and submitted the following forecasts to the German and
Polish Forecast Hub: 1) a direct human forecast (henceforth called
``crowd forecast''), elicited from participants through a web
application {[}31{]} and 2) two semi-mechanistic model-based forecasts
(``renewal model'' and ``convolution model'') informed by basic
assumptions about COVID-19 epidemiology. While the two semi-mechanistic
forecasts were necessarily shaped by our implicit assumptions and
decisions, they were designed such as to minimise the amount of human
intervention involved. For example, we refrained from adjusting model
outputs or refining the models based on past performance. Forecasts were
created in real time over a period of 21 weeks from October 12th 2020
until March 1st 2021 and submitted to the German and Polish Forecast hub
{[}15,16{]}. All code and tools necessary to generate the forecasts and
make a forecast submission are available in the
\texttt{covid.german.forecasts} R package {[}32{]}. This repository also
contains a record of all forecasts submitted to the German and Polish
Forecast Hub. Forecasts were evaluated using a variety of scoring
metrics and compared among each other and against an ensemble of all
other models submitted to the German and Polish Forecast Hub.

\hypertarget{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}{%
\subsection{Forecast targets and interaction with the German and Polish
Forecast
Hub}\label{forecast-targets-and-interaction-with-the-german-and-polish-forecast-hub}}

The German and Polish Forecast Hub (now mostly merged into the {[}17{]})
elicits predictions for various COVID-19 related forecast targets from
different research groups every week. Forecasts had to be made every
Monday (with submissions allowed until Tuesday 3pm) and were permitted
to use any data that was available by Monday 11.59pm. We submitted
forecasts for incident and cumulative weekly reported numbers of cases
of and deaths from COVID-19 on a national level in Germany and Poland
over a one to four week forecast horizon. Forecasts were submitted on
Mondays, but weeks were defined as ending on a Saturday (and starting on
Sunday), meaning that forecast horizons were in fact 5, 12, 19 and 26
days. Submissions were required in a quantile-based format with 23
quantiles of each output measure at levels 0.01, 0.025, 0.05, 0.10,
0.15, \ldots, 0.95, 0.975, 0.99. Forecasts submitted to the Forecast Hub
were combined into different ensembles every week, with the median
ensemble (i.e., the \(\alpha\)-quantile of the ensemble is given by the
median of all submitted \(\alpha\)-quantiles) being the default ensemble
shown on all official Forecast hub visualisations
(https://kitmetricslab.github.io/forecasthub/forecast).

Data on daily reported test positive cases and deaths linked to COVID-19
were provided by the organisers of the German and Polish Forecast hub.
Until December 14th, 2020, these data were sourced from the European
Centre for Disease Control {[}33{]}. After ECDC stopped publishing daily
data, observations were sourced from the Robert Koch Institute (RKI) and
the Polish Ministry of Health for the remainder of the submission period
{[}34{]}. These data are subject to reporting artefacts, (such as for
example delayed case reporting in Poland on the 24th November,
{[}35{]}), changes in reporting over time, and variation in testing
regimes (for example in Germany from the 11th of November on, {[}36{]}).
The ECDC data as well as the data published by the Polish Ministry of
Health were also subject to data revisions, although most of them (with
a notable exception of a data update for October 12 2020 in Germany)
only affected daily, not weekly data (see Figures
\ref{fig:daily-truth-update} and \ref{fig:weekly-truth-update}).

\hypertarget{crowd-forecasts}{%
\subsection{Crowd forecasts}\label{crowd-forecasts}}

Our crowd forecasts were created as an ensemble of forecasts made by
individual participants every week through a web application
(https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Weekly forecasts had
to be submitted before Tuesday 12pm every week, but participants were
asked to only use any information or data that was already available by
Monday night. The application was built using the \texttt{shiny} and
\texttt{golem} R packages {[}37,38{]} and is available in the
\texttt{crowdforecastr} R package {[}31{]}. To make a forecast in the
application participants could select a predictive distribution (with
the default being log-normal) to represent the probability that the
forecasted quantity took certain values. Median and width of the
uncertainty could be adjusted by either interacting with a figure
showing their forecast or providing numerical values (see screenshot in
Figure \ref{fig:screenshot} in the SI). The default shown was a
repetition of the last known observation with constant uncertainty
around it computed as the standard deviation of the last four changes in
weekly log observed forecasts (i.e.~as
\(\sigma(log(value4) - log(value3), log(value3) - log(value2), \ldots )\)).
A comparison of the crowd forecasts against the default baseline shown
in the application is displayed in Figure \ref{fig:compare-forecasters}
in the Appendix. Our interface also allowed participants to view past
observations based on the hub data, as well as their forecasts, on a
logarithmic scale and presented additional contextual COVID-19 data
sourced from {[}39{]}. These data included, for example, notifications
of both test positive COVID-19 cases and COVID-19 linked deaths and the
number of COVID-19 tests conducted over time. From November 26 2020 on
we displayed weekly small reports with a visualisation of past forecasts
and scores on our website, epiforecasts.io.

Forecasts were stored in a Google Sheet and downloaded, cleaned and
processed every week for submission to the Forecast Hub. If a forecaster
had submitted multiple predictions for a single target, only the latest
submission was kept. Information on the chosen distribution as well as
the parameters for median and width were used to obtain the required set
of 23 quantiles from that distribution. Forecasts from all forecasters
were then aggregated using an unweighted quantile-wise mean (i.e., the
\(\alpha\)-quantile of the ensemble is given by the mean of all
submitted \(\alpha\)-quantiles). To avoid issues with users trying out
the app and submitting a random forecast, we required that a forecaster
needed to make a forecast for at least two targets for a given forecast
in order to be included in the crowd forecast ensemble. On a few
occasions we deleted forecasts that were clearly the result of a user or
software error (such as for example forecasts that were zero
everywhere).

individual forecasts were assessed as clearly erroneous by visual
inspection and subsequently removed before aggregation and were excluded
from the submission as well as the analysis.

Participants were recruited mostly within the Centre of Mathematical
Modeling of Infectious Diseases at the London School of Hygiene \&
Tropical Medicine, but participants were also invited personally or via
social media to submit predictions. Depending on whether they had a
background in either statistics, forecasting or epidemiology,
participants were asked to self-identify as `experts' or `non-experts'.

The study was approved by the Observational / Interventions Research
Ethics Committee at the London School of Hygiene \& Tropical Medicine,
LSHTM Ethics Reference: 22290. Formal consent from participants was
taken in written form through the web application.

\hypertarget{model-based-forecasts}{%
\subsection{Model-based forecasts}\label{model-based-forecasts}}

We used two Bayesian semi-mechanistic models from the \texttt{EpiNow2} R
package (version 1.3.3) as our model-based forecasts {[}40{]}. The first
of these models, here called ``renewal model'', used the renewal
equation {[}41{]} to predict reported cases and deaths (see details in
the SI). It estimated the effective reproduction number \(R_t\) (the
average number of people each person infected at time t is expected to
infect in turn) and modelled future infections as a weighted sum of past
infection multiplied by \(R_t\). \(R_t\) was assumed to stay constant
beyond the forecast date, roughly corresponding to continuing the latest
exponential trend in infections. On the 9th of November we altered the
date when \(R_t\) was assumed to be constant from two weeks prior to the
date of the forecast to the forecast date, which we found to yield a
more stable \(R_t\) estimate. Reported case and death notifications were
obtained by convolving predicted infections over data-based delay
distributions {[}40,42--44{]} to model the time between infection and
report date. The renewal model was used to predict cases as well as
deaths with forecasts being generated for each target separately. Death
forecasts from the renewal model were therefore not informed by past
cases. One submission of the renewal model on December 28th 2020 was
delayed and therefore not included in the official Forecast hub
ensemble.

The second model (``convolution model'', see details in SI) was only
used to forecast deaths and was added later, starting December 7th 2020
(with the first forecast from December 7th suffering from a software bug
and therefore disregarded in all further analyses). The convolution
model was submitted, but never included in the official Forecast hub
ensemble due to concerns that it could be too similar to the renewal
model. The convolution model predicted deaths as a fraction of infected
people who would die with some delay, by using a convolution of reported
cases with a distribution that described the delay from case report to
death and a scaling factor (the case-fatality ratio). Both the renewal
and the convolution model used daily observations and assumed a negative
binomial observation model with a multiplicative day-of-the-week effect
{[}40{]}.

Line list data used to inform the prior for the delay from symptom onset
to test positive case report or death in the model-based forecasts was
sourced from {[}45{]} with data available up to the 1st of August. All
model fitting was done using Markov-chain Monte Carlo (MCMC) in stan
{[}46{]} with each location and forecast target being fitted separately.

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

For the main analysis we focused mostly on two week ahead forecasts, as
COVID-19 forecasts, especially for cases, were in the past found to have
poor predictive performance beyond this horizon {[}15{]}. Forecasts for
cases were scored using the full period from October 2020 until March
2021. To ensure comparability between models, all death forecasts were
scored using only the period from December 14th on, where all models
including the convolution model were available. To ensure robustness of
our results we conducted a sensitivity analysis where all forecasts
(including cases) were scored only over the later period for which all
forecasts were available (see Section \ref{sensitivity-analysis} in the
SI). Results remained broadly unchanged.

Forecasts were analysed using the following scoring metrics: The
weighted interval score (WIS) {[}47{]}, the absolute error, relative
bias, and empirical coverage of the 50\% and 90\% prediction intervals.
The WIS is a proper scoring rule {[}48{]}, meaning that in expectation
the score is optimised by reporting a predictive distribution that is
identical to the true data-generating distribution. Forecasters are
therefore incentivised to report their true belief about the future. The
WIS can be understood as a generalisation of the absolute error to
quantile-based forecasts (also meaning that smaller values are better)
and can be decomposed into three separate penalties: forecast spread
(i.e.~uncertainty of forecasts), over-prediction and under-prediction.
While the over- and under-prediction components of the WIS capture the
amount of over-prediction and under-prediction in absolute terms, we
also look at a relative tendency to make biased forecasts. The bias
metric {[}9{]} we use captures how much probability mass of the forecast
was above or below the true value (mapped to values between -1 and 1)
and therefore represents a general tendency to over- or under-predict in
relative terms. A value of -1 implies that all quantiles of the
predictive distribution are below the observed value and a value of 1
that all quantiles are above the observed value. Empirical coverage is
the percentage of observed values that fall inside a given prediction
interval (e.g.~how many observed values fall inside all 50\% prediction
intervals). Scoring metrics are explained in more detail in Table
\ref{tab:scoring-metrics} in the SI. All scores were calculated using
the \texttt{scoringutils} R package {[}49{]}.

At all stages of the evaluation our forecasts were compared to the
median ensemble of all \emph{other} models submitted to the German and
Polish Forecast Hub (``Hub ensemble''). This ``Hub ensemble'' was
retrospectively computed and excludes all our models, leaving on average
five ensemble member models (see details in Section
\ref{contributions-hub}, as well as in Table
\ref{tab:table-ensemble-versions} and Figure
\ref{fig:num-ensemble-members} in the SI). What we call ``Hub ensemble''
in this article therefore differs from the ``official Hub ensemble''
(here called ``hub-ensemble-realised'') which included crowd forecasts
as well as renewal model forecasts. To enhance interpretability of
scores we mainly report WIS relative to the Hub ensemble in the main
text, i.e.~we divided the average scores for a given model by the
average score achieved by the Hub ensemble on the same set of forecasts
(with values \textgreater1 implying worse and values \textless1 implying
better performance than the Hub ensemble). In addition to comparing our
forecasts against the hub ensemble excluding our models, we also
assessed the impact of our forecasts on the performance of the
forecasting hub by recalculating separate versions of the Hub ensemble
with only some (or all) of our forecasts included. Versions that
included either all of our models (``hub-ensemble-with-all'') or only
one of them (``hub-ensemble-with-X'') were computed retrospectively.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{crowd-forecast-participation}{%
\subsection{Crowd forecast
participation}\label{crowd-forecast-participation}}

A total number of 32 participants submitted forecasts, 17 of those
self-identified as `expert' in either forecasting or epidemiology. The
median number of forecasters for any given forecast target was 6, the
minimum 2 and the maximum 10. The mean number of submissions from an
individual forecaster was 4.7 but the median number was only one - most
participants dropped out after their first submission. Only two
participants submitted a forecast every single week, both of whom are
authors on this study.

\begin{figure}[H]
%\includegraphics[width=1\linewidth,]{../analysis/plots/aggregate-performance-all-v4} 
\caption{Visualisation of aggregate performance metrics for forecasts one to four weeks into the future. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\% prediction intervals (50\% coverage is perfect). D: Empirical coverage of the 90\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons}\label{fig:agg-performance-all}
\end{figure}

\begin{figure}[H]
%\includegraphics[width=1\linewidth,]{../analysis/plots/figure-forecasts-2} 
\caption{Two week ahead forecasts and corresponding scores. A, C: Visualisation of 50\% prediction intervals of two week ahead forecasts against the reported values. Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS.}\label{fig:forecasts-and-truth}
\end{figure}

\hypertarget{case-forecasts}{%
\subsection{Case Forecasts}\label{case-forecasts}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.3cm}}
\toprule
Name & Explanation\\
\midrule
\endfirsthead
\multicolumn{2}{@{}l}{\textit{(continued)}}\\
\toprule
Name & Explanation\\
\midrule
\endhead
